---
description: "Kruul gick ned f칬r f칬rsta g친ngen"
date: 2025-10-29
image: https://res.cloudinary.com/dhmmkvcpy/image/upload/t_250x100/thumb/kruul
footer: "Veckobladet 44 (2025) - [游 Tillbaka till hemsidan](https://www.fika-guild.xyz)"
format: 
  revealjs:
    title-slide: false
    theme: veckobladet.scss
freeze: true
---
# Veckobladet V.44 2025 {.no-title background-image="https://res.cloudinary.com/dhmmkvcpy/image/upload/q_auto/f_auto/t_1920x1080/bgs/mysteries" }

```{r}
library(here)
here::i_am("veckobladet/V43-2025.qmd")

# Now source your scripts - these should all work
source(here("scripts", "01_database.R"))
# source(here("scripts", "02_registry.R")) 
# source(here("scripts", "03_parser.R"))
# source(here("scripts", "04_data_entry.R"))
source(here("scripts", "05_queries.R")) 
source(here("scripts", "06_presentation.R"))


current_week <- 44
current_year <- 2025

prepare_week_data(current_year, current_week-1)
kara_session <- get_session_id_cached("Kara", current_year, current_week-1)
naxx_session <- get_session_id_cached("Naxx", current_year, current_week-1)  
aq40_session <- get_session_id_cached("AQ40", current_year, current_week-1)
bwl_session <- get_session_id_cached("BWL", current_year, current_week-1)
mc_session <- get_session_id_cached("MC", current_year, current_week-1)

kara_text <- "

Kruul nere f칬r f칬rsta g친ngen
"
kara_notes <- "


"

naxx_text <- "


"

naxx_notes <- "


"

aq_text <- "


"

aq_notes <- "


"

bwl_text <- "


"

bwl_notes <- "
BWL ntoes
"

mc_text <- "


"

mc_notes <- "
mc notes
"
```


{{< include partials/intro.qmd >}}

::: {.notes}
D친 var det onsdag och dags f칬r veckobladet i vanlig ordning.

Detta var f칬rsta veckan med schemat vi t칛nker oss fram친t.
:::

# Changelog {background-video="https://res.cloudinary.com/dhmmkvcpy/video/upload/f_mp4/video/Library_bg.mp4" background-video-loop="true" preload="auto" background-video-muted="true" background-opacity="0.5"}

::: {.patch-notes .auto-rotator}
<!-- Ctrl+h remove regular expression </?(ul|div)> Also replace the first <li> with "- " to get the bullets to work properly. -->
- &nbsp;  <!-- Invisible spacer -->
- &nbsp;  <!-- Invisible spacer -->  
- &nbsp;  <!-- Invisible spacer -->
- &nbsp;  <!-- Invisible spacer -->  
- &nbsp;  <!-- Invisible spacer -->
- &nbsp;  <!-- Invisible spacer -->  
- &nbsp;  <!-- Invisible spacer -->
- &nbsp;  <!-- Invisible spacer -->  
- &nbsp;  <!-- Invisible spacer -->
- &nbsp;  <!-- Invisible spacer -->  
<li><span style="color:#ffbf40">Blooming Bud</span> healing now correctly avoids consuming resources or triggering other effects.</li>
<li><span style="color:#ffbf40">Cloak of Flowing Fire</span>, <span style="color:#ffbf40">Tattered Orcish Shawl</span>, <span style="color:#ffbf40">Tattered Crimson Shabrack</span> and <span style="color:#ffbf40">Drape of Groldan</span> can now be enchanted.</li>
<li>Inventory type corrected for <span style="color:#ffbf40">Shadowblaster</span>.</li>
<li><span style="color:#ffbf40">Krug Skullsplitter</span> will no longer wound himself with <span style="color:#ffbf40">Mortal Strike</span>.</li>
<li><span style="color:#ffbf40">Nippsy's Precision Rifle</span>, <span style="color:#ffbf40">Standard Grade Rifle</span>, <span style="color:#ffbf40">Beasthunter's Blunderbuss</span>, <span style="color:#ffbf40">Zan's Leperification Blaster</span>, <span style="color:#ffbf40">Slag Slugger</span> and <span style="color:#ffbf40">Waterlogged Blunderbuss</span> now benefit from ammo pouches.</li>
<li>Illusions will now be removed upon entering a battleground as well.</li>
<li>Fixed the position of <span style="color:#ffbf40">Mal'adaris</span> so he no longer clips the cart.</li>
<li>Fixed mobs being stuck inside <span style="color:#ffbf40">Widow's Nest</span>.</li>
<li>Fixed several <span style="color:#ffbf40">Corrupted Songflowers</span> that were not functioning properly.</li>
<li>Leaving the arena queue will no longer cause you to leave all battleground queues.</li>
<li>A confirmation dialog now appears when changing <span style="color:#ffbf40">blacksmithing</span> specializations.</li>
<li>New transmog items have been added to the shop and to NPCs <span style="color:#ffbf40">Karlos Fieldings</span>, <span style="color:#ffbf40">Ostantino Villantes</span>, <span style="color:#ffbf40">Rixi Lamour</span>, <span style="color:#ffbf40">Riccarda Thillamore</span>, <span style="color:#ffbf40">Vivi McGoldings</span> and <span style="color:#ffbf40">Stella Verve</span>.</li>
<li>The cannon used in the quest <span style="color:#ffbf40">Death From Below</span> will no longer kill players during the naga attack phase.</li>
<li><span style="color:#ffbf40">Dark Harvest</span> no longer affects Affliction spells cast by other Warlocks.</li>
<li>Pet Command <span style="color:#ffbf40">Take Position</span> can no longer be used while mounted.</li>


:::

::: {.notes}

:::


# F칬reg친ende vecka {background-video="https://res.cloudinary.com/dhmmkvcpy/video/upload/f_mp4/video/CoT_bg.mp4" background-video-loop="true" preload="auto" background-video-muted="true" background-opacity="0.5"}

```{r}
#| echo: false
#| results: asis
schedule <- list(
  list(day = "Onsdag", time = "20:00", title = "Chill MC", img = "mc.png"),
  list(day = "Torsdag", time = "20:00", title = "救Kara40", img = "returntokara.png"),
  list(day = "Fredag", time = "20:90", title = "BWL", img = "bwl.png"),
  list(day = "L칬rdag", time = "20:00", title = "AQ40", img = "aq40.png"),
  list(day = "S칬ndag", time = "20:00", title = "救Kara40", img = "returntokara.png"),
  list(day = "M친ndag", time = "20:00", title = "Chill ZG", img = "zg.png"),
  list(day = "Tisdag", time = "19:30", title = "Naxx", img = "naxx.png")
)
cat(schedule_presentation(schedule))
```

::: {.notes}

:::


```{r}
#| echo: false
#| results: asis
if (!is.null(kara_session)) {
  message("Including Kara partial, session: ", kara_session)
  res <- knitr::knit_child(here("veckobladet", "partials", "kara.qmd"), quiet = TRUE)
  cat(res, sep = '\n')
}
if (!is.null(naxx_session)) {
  res <- knitr::knit_child(here("veckobladet", "partials", "naxx.qmd"), quiet = TRUE)
  cat(res, sep = '\n')
}
if (!is.null(aq40_session)) {
  res <- knitr::knit_child(here("veckobladet", "partials", "aq.qmd"), quiet = TRUE)
  cat(res, sep = '\n')
}
if (!is.null(bwl_session)) {
  res <- knitr::knit_child(here("veckobladet", "partials", "bwl.qmd"), quiet = TRUE)
  cat(res, sep = '\n')
}
if (!is.null(mc_session)) {
  res <- knitr::knit_child(here("veckobladet", "partials", "mc.qmd"), quiet = TRUE)
  cat(res, sep = '\n')
}
```


# Kommande vecka {background-video="https://res.cloudinary.com/dhmmkvcpy/video/upload/f_mp4/video/ToK_bg.mp4" background-video-loop="true" preload="auto" background-video-muted="true" background-opacity="0.5"}

```{r}
#| echo: false
#| results: asis
schedule <- list(
  list(day = "Onsdag", time = "20:00", title = "Chill MC", img = "mc.png"),
  list(day = "Torsdag", time = "20:00", title = "救Kara40", img = "returntokara.png"),
  list(day = "Fredag", time = "20:90", title = "BWL", img = "bwl.png"),
  list(day = "L칬rdag", time = "20:00", title = "AQ40", img = "aq40.png"),
  list(day = "S칬ndag", time = "20:00", title = "救Kara40", img = "returntokara.png"),
  list(day = "M친ndag", time = "20:00", title = "Chill ZG", img = "zg.png"),
  list(day = "Tisdag", time = "19:30", title = "Naxx", img = "naxx.png")
)
cat(schedule_presentation(schedule))
```
